---
title: "Gender_bias"
author: "Thea Rolskov Sloth"
date: "12/11/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Getting packages
```{r loading packages, include = FALSE}
library(pacman)
p_load(brms, tidyverse, tidybayes, ggplot2, LaplacesDemon, rethinking, tidyr, reshape2, tibble, plotly, jpeg, tm, ggrepel, utils)
```

#Setting directory
```{r}
setwd("~/Bachelor-MM-/") #TRS
```

#Loading data
```{r}
data_ib <- read.csv("implicit_bias/data_ib.csv")[,2:12]
data_eb <- read.csv("explicit_bias/eb_results.csv")[, 2:6]
data_db <- read.csv("decision_bias/disagree_sensitivity_db_long.csv")[, 2:44]
data_db_all <- read.csv("decision_bias/data_db_all.csv")
```

#Creating new data frame with relevant variables for gender bias
```{r}
#Selecting age, gender, ID
data_gb <- unique(data_ib[, 1:3])

#Adding rt dif
data_gb$rt_dif <- as.data.frame(ranef(model_ib1))[, 5]

#Adding sexism scores
data_gb <- merge(data_gb, data_eb)

#adding random effect of decision bias 
data_gb$DB <- as.data.frame(ranef(model_db2_ID))[, 5]
data_gb$DB_skill <- as.data.frame(ranef(model_db2_ID))[, 13] - as.data.frame(ranef(model_db2_ID))[, 9]
data_gb$DB_conf <- 

```

#Network analysis
MvBind(Ex_bs, Ex_hs, Im_b, D_b, D_b_skill, D_b_confidence) ~ 1 + Gender + (1|p|ID)
P is a parameter, you can write whatever
Prior(LKJ(5), class =cor)
Prior that makes sense for correlations
Will get three values  	, which will explain the correlation between the variables


#Make network plot
