---
title: "Simulation_preparation"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



```{r working directory and data and library}
library(pacman)
p_load(brms, tidyverse, tidybayes, ggplot2, LaplacesDemon, rethinking, tidyr, reshape2, tibble, plotly, jpeg, tm, ggrepel, utils, boot, Hmisc, scales)

setwd("~/Bachelor-MM-/") #TRS

data_eb <- read.csv("explicit_bias/eb_results.csv")[, 2:6]
data_ib <- read.csv("implicit_bias/data_ib.csv")[,2:12]
```


###Implicit bias 

```{r prepare filtered dataframe}
female_names <- c("Josefine", "Line", "Mette", "Ruth", "Birthe", "Camilla", "Hanne" )
male_names <- c("Sebastian", "Ole", "Casper", "Jens", "Mikkel", "Rasmus", "Morten")
career_items <- c("Virksomhed", "Løn", "Kontor", "Karriere", "Akademiker", "Ledelse", "Handel")

data_ib_filtered_incongruent <- filter(data_ib, (block == 3 | block == 4) & (word %in% female_names | word %in% career_items))
data_ib_filtered_congruent <- filter(data_ib, (block == 6 | block == 7) & (word %in% male_names | word %in% career_items))


data_ib_filtered <- rbind(data_ib_filtered_congruent, data_ib_filtered_incongruent)
```

```{r model with filtered data}
#Tranforming condition to a factor
data_ib_filtered$condition <- as.factor(data_ib_filtered$condition)

#to figure out which prior we need to make
get_prior(rt_log ~ condition*gender + (condition|ID), data = data_ib_filtered)

#Defining a prior 
prior_ib2.2 = c(prior(normal(-0.4, 0.2), class = "Intercept"), 
          prior(normal(0, 0.2), class = "b"), 
          prior(normal(0, 0.2), class = "sigma"),
          prior(normal(0, 0.1), class = "sd"))

#Implicit model
model_ib2.2_prior <- brm(rt_log ~ condition*gender + (condition|ID),
                    data = data_ib_filtered,
                    family = gaussian(),
                    prior = prior_ib2.2,
                    sample_prior = "only",
                    cores = 2,
                    chains = 2)

pp_check(model_ib2.2_prior, nsamples = 100) #Doing a predictive prior check to test priors

model_ib2.2 <- brm(rt_log ~ condition*gender + (condition|ID),
                    data = data_ib_filtered,
                    family = gaussian(),
                    prior = prior_ib2.2,
                    sample_prior = TRUE,
                    iter = 5000,
                    warmup = 2000,
                    cores = 4,
                    chains = 4)

summary(model_ib2.2)

#plotting
plot(model_ib2.2)

marginal_effects(model_ib2.2)
```

###Extracting the EB to the simulation

  For the explicit task: The sexism score we have range on a scale from 0 to 6. 0 indicating no sexist behaviour, 6 highly sexist behaviour. As most questions ask about women in relation to men, we have thought of setting the 0 as the bias towards men and the hostile, benevolent or combined score as the bias towards women. But this might be very constructed as there is no possibility of disfavoring men.
   Do you have an idea of how to extract biases from this measure?

In abstract, somebody w 0 would have the same "bias" for men and women (1, and 1, let's say), right? So no, there is no way to model a bias against men. That's a limit of the measure, to be discussed. On the other hand, if these measures correlate with other biases (e.g. implicit and db), you can say it's capturing something (and we have good prior info about sexism being disproportionally against women).
How to define the simulation bias from this? Let's define a pavement bias: 0? 0.5? You then rescale the scores so that 6 is the lowest value and 0 is 1.

```{r}
#Defining 0.5 as the baseline based on the theory, which states that pariticpants rarely use extreme values in scales. Thus, if you answer the question in the direction of non-sexist using either the most extreme or the second most extreme possibility, you roughly get a score around 0.5. 

data_eb_r = data_eb

#Reverting the scores, making a score of 5 a score of 0 and visa versa
data_eb_r$overall_score <- 5 - data_eb_r$overall_score
data_eb_r$benevolent_score <- 5 - data_eb_r$benevolent_score
data_eb_r$hostile_score <- 5 - data_eb_r$hostile_score

#Subtracting the pavement bias of 1
data_eb_r$overall_score <- data_eb_r$overall_score + 1.5
data_eb_r$benevolent_score <- data_eb_r$benevolent_score + 1.5
data_eb_r$hostile_score<- data_eb_r$hostile_score + 1.5

#Make everything over 5 to 5
data_eb_r$overall_score <- ifelse(data_eb_r$overall_score < 5, data_eb_r$overall_score, 5) 
data_eb_r$benevolent_score <- ifelse(data_eb_r$benevolent_score < 5, data_eb_r$benevolent_score, 5) 
data_eb_r$hostile_score<- ifelse(data_eb_r$hostile_score < 5, data_eb_r$hostile_score, 5) 

#scaling to values to a scale ranging from 0-1
data_eb_r$overall_score <- rescale(data_eb_r$overall_score, to = c(0, 1.0), from = range(0,5))
data_eb_r$benevolent_score <- rescale(data_eb_r$benevolent_score, to = c(0, 1.0), from = range(0,5))
data_eb_r$hostile_score <- rescale(data_eb_r$hostile_score, to = c(0, 1.0), from = range(0,5))


#Rerunning the model to get new estimates

#Defining a prior, mean set to 0.5 because best conceptual meaning
prior_eb1_scaled = c(prior(normal(0.8, 0.1), class = "Intercept"), 
          prior(normal(0, 0.1), class = "b"), 
          prior(normal(0, 0.1), class = "sigma"),
          prior(normal(0, 0.05), class = "sd"))

#explicit model
model_eb1_scaled <- brm(overall_score ~ gender + (1|ID),
                    data = data_eb_r,
                    family = gaussian(),
                    prior = prior_eb1_scaled,
                    sample_prior = "only",
                    cores = 2,
                    chains = 2)

#prior check 
pp_check(model_eb1_scaled, nsamples = 100) #Doing a predictive prior check to test priors

#models
model_eb1_scaled <- brm(overall_score ~ gender + (1|ID),
                    data = data_eb_r,
                    family = gaussian(),
                    prior = prior_eb1_scaled,
                    sample_prior = TRUE,
                    iter = 8000,
                    warmup = 4000,
                    cores = 4,
                    chains = 6, 
                    seed = 123,
                    control = list(adapt_delta = 0.999))


```


