---
title: "Preprocessing, Implicit"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


#Getting packages
```{r loading packages, include = FALSE}
library(pacman)

p_load(brms, tidyverse, tidybayes, ggplot2, LaplacesDemon, rethinking, tidyr, reshape2, tibble, plotly, jpeg, tm)
```

#Setting working directory
```{r}
setwd("~/Bachelor-MM-/implicit_bias") #TRS
```

#Loading data
```{r loading data}
#path_ib = "~/Cognitive Science/5. Semester/Bachelor, MM/GIT/Bachelor-MM-/implicit_bias/implicit_data/" #KK
path_ib = "implicit_data/" #TRS

#Listing files in path
files <- list.files(path = path_ib)

#Create empty data frame
data_ib <- data.frame(matrix(ncol = 10, nrow = 0))

#Looping through data files and inserting in dataframe
for (i in files) {
  d <- read.delim(file = paste(path_ib, i, sep = ""), sep = ",", header = TRUE)
  data_ib = rbind(data_ib,d)
}

#removing first column
data_ib <- data_ib[, 2:10]
```

#Subsetting data from conditions with four categories
```{r}
data_ib <- subset(data_ib, block == 3 | block == 4 | block == 6 | block == 7)
```

#Adding a column with condition: 1 = Incongruent, 0 = Congruent
```{r}
data_ib$condition <- 0 

data_ib[data_ib$block == 3,]$condition <- 1
data_ib[data_ib$block == 4,]$condition <- 1
data_ib[data_ib$block == 6,]$condition <- 0
data_ib[data_ib$block == 7,]$condition <- 0

```

#Remove first two trials of each block 
```{r}
data_ib <- filter(data_ib, trial != c(1, 2))
```

#Creating rt cut-off
```{r}
#Creating cut-offs
data_ib$rt[data_ib$rt > 3] <- NA
data_ib$rt[data_ib$rt < 0.3] <- NA

#how many trials are removed?
table(data_ib$rt > 3)
table(data_ib$rt < 0.3)

```

#Log-transforming RT-data
```{r}
data_ib$rt_log <- log(data_ib$rt)
```

#Removing rows including NA's
```{r}
data_ib <- na.omit(data_ib) 
```

#calculate difference in average speed per participant using  B4 & B7 and B3 & B6
```{r}
#Creating new dataframe for reaction times
meanrt <- data.frame(matrix(ncol=3))

#Making a loop to go through participants and blocks and calculate mean rt
n=1

#average rt per participant per block 
for (i in unique(data_ib$ID)){
  for (x in unique(data_ib$block)){
    tempdata <- subset(data_ib, ID==i & block==x)
    meanrt[n,1] <- i
    meanrt[n,2] <- x
    meanrt[n,3] <- mean(tempdata$rt)
    n=n+1
  }
}

#Renaming column names
colnames(meanrt) <- c("ID", "block", "mean_rt")

```

#Calculating error rate
```{r}
#Creating a table of correct and incorrect first press errors
table(data_ib$correct)

#Calculating the error rate overall in percentage
416/7056*100

#Calculating individual error rate
error_rate <- data_ib %>%group_by(ID) %>% summarise(error_rate = (NROW(trial)-sum(correct))/NROW(trial))

#Investigating the error rate
range(error_rate$error_rate)
hist(error_rate$error_rate)
mean(error_rate$error_rate)
```

#Removing incorrect trials
```{r}
data_ib <- filter(data_ib, correct == 1)
```


#Create CSV
```{r}
write.csv(data_ib, file = "data_ib.csv")
```



